Fuel switch, savings, electrification - Decarbonisation in industry OR Pathways to Carbon Neutral Industrial Sectors: Integrated Modelling Approach with High Level of Detail for End-use Processes OR Decarbonization options in industry and conceptual model of industry in the integrated energy system

### 2018-01-21 article.tex
some wording corrections

The first addition introduced concerns the commodities part of the energy demand: electricity, fuels and heat.
The electricity demand now satisfies, in every single sector, the demand of the single end-uses. This addition facilitates the investigation of decarbonisation options (e.g. savings) at a later stage, as the new options can be applied directly to each end use (\textbf{maybe rewrite, the point here is that the more disaggregated is the consumption, the easier will be to investigate other options to satisfy the demand of decrease the demand}). 
Furthermore, electricity can be either be imported by the grid, or it can be self-produced using small plants. It can also be used to run heat pumps and satisfy the heat demand, or "elevate" the quality of heat, for peculiar processes. 
Heat, previously considered only as district heat demand, now includes three temperature levels: space heating, process heat low temperature and process heat high temperature processes.

@@

\subsection{Overview Data Sources and Processing}
The Danish case study is based on the following main datasets:
\begin{itemize}
 \item Yearly Danish energy usage by industrial group (db117-grouping) and fuel type (..different fuels)
 \item End-use connected to fuel type and industry groupings for a specific year (2012) 
 \item Danish companies including address, industry group and number of employees
 \item Adress database connecting the address to geographic location
 \item Geographic location and extension of district heat areas
 \item Conversion potential for electrification and biomass in shares per industry grouping
 \item Hourly gas consumption profiles of gas consumers including the information of the industry group affiliation
\end{itemize}

As far as possible, openly available data was chosen for the case study. Like that results can be scrutinized based on the open soucre code and open sources. However, consumer profiles can only be published in aggregated form.

For data processing, the python packages pandas and numpy were utilized, which dataframe structure is especially suited for processing and combination of different data source wiht a satisfactory speed performance. With the objective of achieving a high re-usability and flexibility of data and scripts, the processing was modularized and split in different steps. Between the scripts, intermediate dataframes are passed. This makes the processing more efficient, since some dataframes have to be applied by different subsequent steps. This flow is illustrated in Figure ...

@@

\subsection{Energy use}
The energy consumption by industry group and fuel type is published by Statistics Denmark on a yearly basis. This data is reliably and continously available and the structure of the industry grouping follows the db117-code which is widely applied for identifying the affiliation of companies and utilized in other data sources about the conversion potential in industry. From that dataset, public service, building and mining was excluded.

On the end-use side, transport of all industry groups is excluded from the dataset and the case study focuses on electricity and heat demand. The required temperature level is decisive for which conversion options are available to reduce the use of fossil fuels. The allocation of the fuel usage in industry to different end-use categories is available for the year 2012 from the ... for a large part of Danish industry. The absolute fuel consumption numbers per end-use, fuel and industry group were converted to shares relating to industry groups and fuel usage. Due to the fact that the industry groups were choses slightly different than in Statistics Danmarks, this had to be accounted for. Also, fuels and industry grouping had to be aligned. This calculation can be applied to each available year of the Statistics Denmark data, so that after this calculation step the energy usage per industry group, fuel and end-use is available for different years. It has to be mentioned that the division has to be adapted if the end-use within an industry group changes significantly. Growth of industry groups and thus energy usage increase would be divided by the same end-use allocation.

Derived from the conceptual model, we group the end-use heat demand into space heat, process heat low and process heat high. This was considered detailed enough to caputure the main differences between the conversion option while still modelwise manageable. ...end-use heat categories were available from the main data, which are - depending on their required temperature level aggregated as displayed in Table ...

\begin{table}
\begin{tabular}{l | c | c}
End-use & Temperature level [$^{\circ}$C] & Model heat type\\
\hline \hline
Space heating & 50-90 & space  \\ 
Distillation & 50-100 & process low \\
Heating/Boiling & mostly 70-110 & process low \\
Drying & about 100 & process low \\
Inspissation & 130 & process low \\ 
Burning/Sintering & more than 250 & process high \\ 
Melting/Casting & more than 300 & process high  
\end{tabular}
\caption{Clustering end-use by heat level. Source for process heat levels: \cite{VM2015}}
\end{table}

@@

It is not only necessary to determine which part of industrial energy demand and excess heat can be connected to district heat in general, but also to which district heat area. Following the logic of the model Balmorel, heat can just be distributed within an Area in Balmorel. If the geographical relation between heat source and heat demand would disregarded, the effort of matching heat demand and supply temporarily would be underestimated and the potentials for district heat and usage of excess heat overestimated. The modelled Balmorel Areas in our case relate to aggregations of real Danish district heat areas. The more than 200 district heat areas are aggregated to 36 Areas for the model input. Connected district heat areas are aggregated. Small rural district heat areas are also summarized for Denmark East and Denmark West. This aggregation is a compromise between model complexity / calculation time and accurancy. Since mostly small areas are summarized, the effect on the results is minor.

@@

The basis this localalisation is the list of companies located in Denmark which includes addresses, affiliation to detailed industry group and number of employees information \cite{virk2017}. Entries that did not have any employees reduced the list from .... to .... The geographic location (coordinates) for the remaining were derived by matching the addresses to an address list containing coordinates \cite{}. This was done via a matching operation in python. \textit{State how much could not be located here?} District heat areas in Denmark are provided publicly from .... as a shapefile \cite{kortforsyningen2017} and were aggregated to the 36 areas as described in \cite{Petrovic2014} \textit{something to cite from Amalia?}. Via the coordinate information, the companies were assigned an area with a spatial join operation in the geographical software QGIS.

@@

\includegraphics[scale=0.36]{img/DK_DH_Balmorel_areas2_DH_share_SH.png}
\caption{Space heat demand of companies supplied by district heat. Own calulations based on: \cite{kortforsyningen2017,virk2017,Buhler2017,Petrovic2014,VM2015,StatisticsDenmark2016}}

\includegraphics[scale=0.36]{img/DK_DH_Balmorel_areas2_DH_share_PHL.png}\\
\caption{Low process heat demand supplied by district heat. Own calulations based on: \cite{kortforsyningen2017,virk2017,Buhler2017,Petrovic2014,VM2015,StatisticsDenmark2016}}
\fi
A similar approach is applied to derive the demand profiles per area. For each area, one process heat and one space heat profile is generated based on the shares the main industry groups Service, Production single, Production double and Production triple have in the industrial process and space heat demand of the area.

@@

\section{Preliminary outcomes and discussion} \label{outcdisc}
% Results should be clear and concise.
Concluding the numbers. This I know how to calculate:
\begin{itemize}
    \item How much industry already uses district heat?
    \item How much industry already uses heat pumps?
    \item How high is the potential for more industry using district heat?
    \item Which percentage/amount of fossil fuel/installed capacity can be electrified to which cost in which industry group (DGC-data)?
    \item What is the fuel switch options to which cost: Maybe we should have a table with the sectors and end-uses their options to decarbonize.
\end{itemize}
This would be nice to get, but probably only modelling possible:
\begin{itemize}
    \item electricity, process, space heat saved
    \item process, space heat electrified
    \item fuel switched
    \item district heating utilized by industry
    \item excess heat utilized additionally from industry
    \item costs
    \item emissions saved
    \item sensitivities
\end{itemize}

>>>>

The first addition introduced concerns the commodities part of the energy demand: electricity, fuels and heat.
The electricity demand now satisfies, in every single sector, the demand of the single end-uses. This addition facilitates the investigation of decarbonisation options (e.g. savings) at a later stage, as the new options can be applied directly to each end use (\textbf{maybe rewrite, the point here is that the more disaggregated is the consumption, the easier will be to investigate other options to satisfy the demand of decrease the demand}). 
Furthermore, electricity can be either be imported by the grid, or it can be self-produced using small plants. It can also be used to run heat pumps and satisfy the heat demand, or "elevate" the quality of heat, for peculiar processes. 
Heat, previously considered only as district heat demand, now includes three temperature levels: space heating, process heat low temperature and process heat high temperature processes. As an example how processes are categorised to these heat groups, Table \label{tab:temperature_levls} summarises the categorisation is done in the case study.

@@

\subsection{Overview Data Sources and Processing}
The Danish case study is based on the following main datasets:
\begin{itemize}
 \item Yearly Danish energy usage by industrial group (db117-grouping) and fuel type (..different fuels)
 \item End-use connected to fuel type and industry groupings for a specific year (2012) 
 \item Danish companies including address, industry group and number of employees
 \item Address database connecting the address to geographic location
 \item Geographic location and extension of district heat areas
 \item Conversion potential for electrification and biomass in shares per industry grouping
 \item Hourly gas consumption profiles of gas consumers including the information of the industry group affiliation
\end{itemize}

As far as possible, openly available data was chosen for the case study. Like that results can be scrutinised based on the open source code and open sources. However, consumer profiles can only be published in aggregated form.

For data processing, the python packages pandas and numpy were utilised, which dataframe structure is especially suited for processing and combination of different data source with a satisfactory speed performance. With the objective of achieving a high re-usability and flexibility of data and scripts, the processing was modularised and split in different steps. Between the scripts, intermediate dataframes are passed. This makes the processing more efficient, since some dataframes have to be applied by different subsequent steps. This flow is illustrated in Figure ...

@@

\subsection{Energy use}
The energy consumption by industry group and fuel type is published by Statistics Denmark on a yearly basis. This data is reliably and continuously available and the structure of the industry grouping follows the db117-code which is widely applied for identifying the affiliation of companies and utilised in other data sources about the conversion potential in industry. From that dataset, public service, building and mining was excluded.

On the end-use side, transport of all industry groups is excluded from the dataset and the case study focuses on electricity and heat demand. The required temperature level is decisive for which conversion options are available to reduce the use of fossil fuels. The allocation of the fuel usage in industry to different end-use categories is available for the year 2012 from the ... for a large part of Danish industry. The absolute fuel consumption numbers per end-use, fuel and industry group were converted to shares relating to industry groups and fuel usage. Due to the fact that the industry groups were chosen slightly different than in Statistics Danmarks, this had to be accounted for. Also, fuels and industry grouping had to be aligned. This calculation can be applied to each available year of the Statistics Denmark data, so that after this calculation step the energy usage per industry group, fuel and end-use is available for different years. It has to be mentioned that the division has to be adapted if the end-use within an industry group changes significantly. Growth of industry groups and thus energy usage increase would be divided by the same end-use allocation.

Derived from the conceptual model, we group the end-use heat demand into space heat, process heat low and process heat high. This was considered detailed enough to capture the main differences between the conversion option while still model-wise manageable. ...end-use heat categories were available from the main data, which are - depending on their required temperature level aggregated as displayed in Table ...

\begin{table}
\begin{tabular}{l | c | c}
End-use & Temperature level [$^{\circ}$C] & Model heat type\\
\hline \hline
Space heating & 50-90 & space  \\ 
Distillation & 50-100 & process low \\
Heating/Boiling & mostly 70-110 & process low \\
Drying & about 100 & process low \\
Inspissation & 130 & process low \\ 
Burning/Sintering & more than 250 & process high \\ 
Melting/Casting & more than 300 & process high  
\end{tabular}
\caption{Clustering end-use by heat level. Source for process heat levels: \cite{VM2015}}
\label{tab:temperature_levls} 
\end{table}

@@

It is not only necessary to determine which part of industrial energy demand and excess heat can be connected to district heat in general, but also to which district heat area. Following the logic of the model Balmorel, heat can just be distributed within an Area in Balmorel. If the geographical relation between heat source and heat demand would disregarded, the effort of matching heat demand and supply temporarily would be underestimated and the potentials for district heat and usage of excess heat overestimated. The modelled Balmorel Areas in our case relate to aggregations of real Danish district heat areas. The more than 200 district heat areas are aggregated to 36 Areas for the model input. Connected district heat areas are aggregated. Small rural district heat areas are also summarised for Denmark East and Denmark West. This aggregation is a compromise between model complexity / calculation time and accuracy. Since mostly small areas are summarised, the effect on the results is minor.

@@

The basis this localisation is the list of companies located in Denmark which includes addresses, affiliation to detailed industry group and number of employees information \cite{virk2017}. Entries that did not have any employees reduced the list from .... to .... The geographic location (coordinates) for the remaining were derived by matching the addresses to an address list containing coordinates \cite{}. This was done via a matching operation in python. \textit{State how much could not be located here?} District heat areas in Denmark are provided publicly from .... as a shape-file \cite{kortforsyningen2017} and were aggregated to the 36 areas as described in \cite{Petrovic2014} \textit{something to cite from Amalia?}. Via the coordinate information, the companies were assigned an area with a spatial join operation in the geographical software QGIS.

@@

\includegraphics[scale=0.36]{img/DK_DH_Balmorel_areas2_DH_share_SH.png}
\caption{Space heat demand of companies supplied by district heat. Own calculations based on: \cite{kortforsyningen2017,virk2017,Buhler2017,Petrovic2014,VM2015,StatisticsDenmark2016}}

\includegraphics[scale=0.36]{img/DK_DH_Balmorel_areas2_DH_share_PHL.png}\\
\caption{Low process heat demand supplied by district heat. Own calculations based on: \cite{kortforsyningen2017,virk2017,Buhler2017,Petrovic2014,VM2015,StatisticsDenmark2016}}
\fi
A similar approach is applied to derive the demand profiles per area. For each area, one process heat and one space heat profile is generated based on the shares the main industry groups Service, Production single, Production double and Production triple have in the industrial process and space heat demand of the area.

@@

\section{Preliminary outcomes and discussion} \label{outcdisc}
% Results should be clear and concise.
Concluding the numbers. This I know how to calculate:
\begin{itemize}
    \item How much industry already uses district heat?
    \item How much industry already uses heat pumps?
    \item How high is the potential for more industry using district heat?
    \item Which percentage/amount of fossil fuel/installed capacity can be electrified to which cost in which industry group (DGC-data)?
    \item What is the fuel switch options to which cost: Maybe we should have a table with the sectors and end-uses their options to decarbonize.
\end{itemize}
This would be nice to get, but probably only modelling possible:
\begin{itemize}
    \item electricity, process, space heat saved
    \item process, space heat electrified
    \item fuel switched
    \item district heating utilised by industry
    \item excess heat utilised additionally from industry
    \item costs
    \item emissions saved
    \item sensitivities
\end{itemize}
